---
title: "R Notebook"
output: html_notebook
---


```{r}
attach(mtcars)
mtcars
```


```{r}
plot(x = wt,y = mpg,
   xlab = "Weight",
   ylab = "Milage",
   xlim = c(1.5,4.5),
   ylim = c(12,35),		 
   main = "Weight vs Milage",abline(lm(mpg~wt)))
```


```{r}
r1 <- c(7,12,28,3,41)
r2 <- c(14,7,6,19,3)
plot(r1,type = "b",col = "red",xlab = "Months", ylab = "Rainfall",main = "Rainfall line chart",pch=19, lty=2)
lines(r2, type = "b", col = "blue",pch=23,lty=6)
```


```{r}
plot(density(mtcars$mpg),main='Density plot of MPG',xlab='MPG',col='green')
```


```{r}
hist(qsec,col="orange",border="red")
```
```{r}
pairs(~wt+mpg+disp+cyl+qsec,data = mtcars, main = "Scatter Plot Matrix")
```


```{r}
freq <- table(mtcars$gear)
labs<-paste(names(freq), "\n", freq, sep="")
pie(freq,main="Pie chart for gear", labels=labs, clockwise=T)
```


```{r}
boxplot(mpg~gear, data = mtcars, xlab = "Gears", ylab = "Miles Per Gallon", main = "Mileage Data")
```


```{r}
boxplot(mpg~gear, data = mtcars, xlab = "Gears", ylab = "Miles Per Gallon", main = "Mileage Data",notch=T,varwidth=T,col=c("red","blue","orange"))
```
```{r}
freq <- table(mtcars$gear)
barplot(freq,main="No. of cars per gear",xlab="No. of gears",ylab="Frequency")
```


```{r}
freq <- table(mtcars$gear)
freq
barplot(freq,main="No. of cars per gear",sub="From mtcars dataset",xlab="No. of gears",ylab="Frequency",horiz=TRUE,names.arg=c("3 gears","4 gears","5 gears"))
```


```{r}
freq <- table(mtcars$vs,mtcars$gear)
freq
barplot(freq,main="Car distribution by gear and vs",sub="From mtcars dataset",xlab="No. of gears",ylab="Frequency",col=c("purple","orange"),legend=rownames(freq))
```


```{r}
freq <- table(mtcars$vs,mtcars$gear)
barplot(freq,main="Car distribution by gear and vs",sub="From mtcars dataset",xlab="No. of gears",ylab="Frequency",col=c("purple","orange"),legend=rownames(freq),beside=TRUE)
```


```{r}
freq <- table(mtcars$gear)
barplot(freq,main="No. of cars per gear",sub="From mtcars dataset",xlab="No. of gears",ylab="Frequency",col="purple")
```


```{r}
library(ggplot2)
diamonds
ggplot(diamonds, aes(x=carat,y=price)) + geom_point(color="blue", shape=5) + ggtitle("Carats vs. Price",subtitle="Scatter plot")
```
```{r}
ggplot(mtcars, aes(x=mpg,y=wt)) + geom_point(color="orange", shape=10,size=9) + ggtitle("Weight vs. Miles per Gallon") + geom_text(label=rownames(mtcars))
```
```{r}
ggplot(mtcars,aes(x=qsec)) + geom_histogram(stat="bin",bins=30,fill="green",color="blue") + ggtitle("qsec frequency",subtitle="Histogram")
```
```{r}
ggplot(mtcars,aes(x=gear)) + geom_histogram(stat="bin",bins=3,fill="purple",color="red") + ggtitle("Gear frequency graph")
```


```{r}
ggplot(mtcars,aes(y=mpg)) + geom_bar(color="red",fill="blue") + ggtitle("Horizontal bar plot")
```
```{r}
ggplot(mtcars,aes(x=mpg)) + geom_density(kernel="gaussian",color="black",fill="white")
```
```{r}
ggplot(mtcars,aes(x=mpg,y=wt)) + geom_area(color="black",fill="blue")
```


```{r}
ggplot(iris,aes(Sepal.Length,Petal.Length,color=Species)) + geom_jitter()
```


```{r}
ggplot(diamonds, aes(x, y)) + xlim(4, 10) + ylim(4, 10) + geom_bin2d()
```
```{r}
ggplot(iris,aes(x=Species,y=Petal.Length)) + geom_boxplot(outlier.color = "orange",outlier.shape = 4,outlier.size = 3)
```
```{r}
ggplot(mtcars, aes(factor(gear),mpg)) +  geom_violin()
```


```{r}
library(ggvis)
attach(mtcars)
mtcars
mtcars %>% ggvis(~wt,~mpg) %>% layer_points()
p <- ggvis(mtcars, x = ~wt, y = ~mpg)
layer_points(p)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
